Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-12-16 demystify.tex
updates

\newtcolorbox{myemphasisbox}{
  enhanced,
  boxrule=1pt, frame hidden,
  %borderline = {1pt}{0pt}{blue!75!black},
  colback=gray!20!white,
  sharp corners
}

@@

%\usepackage{tocloft} % For custom TOC levels

\newcommand{\chapterinfo}[1]{%
  \phantomsection
  \addcontentsline{toc}{chapterinfo}{#1}%
}

\newcommand{\sectioninfo}[1]{%
  \phantomsection
  \addcontentsline{toc}{sectioninfo}{#1}%
}

\newcommand{\subsectioninfo}[1]{%
  \phantomsection
  \addcontentsline{toc}{subsectioninfo}{#1}%
}

@@

\subsection{How much do you cost?}\label{sec:ra-cost}
\sectioninfo{Your entire PhD program costs about \$400K in total, but you \emph{do not} pay for it.}

>>>>

\newtcolorbox{myemphasisbox}{
  enhanced,
  boxrule=1pt, frame hidden,
  colback=gray!20!white,
  sharp corners
}

@@

\newcommand{\chapterinfo}[1]{%
  \phantomsection
  \addcontentsline{toc}{chapterinfo}{\color{black}{#1}}%
}
\newcommand{\sectioninfo}[1]{%
  \phantomsection
  \addcontentsline{toc}{sectioninfo}{\color{black}{#1}}%
}
\newcommand{\subsectioninfo}[1]{%
  \phantomsection
  \addcontentsline{toc}{subsectioninfo}{\color{black}{#1}}%
}

@@

\subsection{How much do you cost?}\label{sec:ra-cost}
\subsectioninfo{Your entire PhD program costs about \$400K in total, but you \emph{do not} pay for it.}
